Methods for Feature Learning and Extraction

### 2017-05-02 paper/tex/Paper.tex
Bib
Start paper 4

In their paper on sparse coding, Bruno Olshausen and David Field utilize the above steps to recreate the visual cortex's functionality to improve image recognition. From their perspective, the brain removes redundancy from the information it receives from the photoreceptors and represents the image as a collection of independent events (Olshausen 3311). Previous research in sparse coding focused on 2-dimensional redundancy reduction, which completely omits curves and other higher dimensional collections seen in natural images. To increase the accuracy of existing sparse coding algorithms, Olshausen and Field explore the creation of a linear strategy that can reduce higher order redundancy.

@@

Finding the best set of basis vectors is analogous to creating a model with a probability distribution of each image ($P(I | \phi$)) that matches the probability distribution of images experienced in nature ($P(I^*)$) (3313). The Kullback-Leibler divergence is used as their reconstruction error, which is defined as:
\begin{align*}
   KL = \int P^*(I) \log \frac{P^*(I)}{P(I | \phi)} dI
\end{align*}
where it is equal to 0 if and only if the two distributions are equivalent. Since the probability distribution of nature is fixed, Olshausen and Field focus on the log likelihood instead. The optimization function thus becomes:
\begin{align*}
   \phi^* = argmax_\phi [ argmax_a \log P(I | a, \phi) P(a) ]
\end{align*}
and the learning rule for the model is:
\begin{align*}
   \Delta \phi_i (x) = \eta (a_i r(x))
\end{align*}
where $r(x)$ is defined as the residual image, or the difference between the output of the machine and the intended output. While their algorithm is quite accurate compared to other similar models, it is also slow and restricted. It assumes a linear image model, which is not always the case in nature. It also only consists of a single layer, preventing it from being as accurate as possible.

@@

Non-negative Matrix Factorization (NMF) is an algorithm that has been around for several years and was the focus of a paper by Daniel Lee and H. Sebastian Seung. Much like the models previously explored, Lee and Seung use the following equation as the basis for NMF:
\begin{align*}
 V \approx WH
\end{align*}
What makes this particular algorithm standout is its constraint. In fact, the constraint is in its very name ? that the matrices in the equation are non-negative. The overall simplicity of this algorithm makes it very simple to implement, despite its increased computation time.

@@

%\bibliographystyle{abbrv}
%\bibliography{../lecture_note}

>>>>

In their paper on sparse coding, Bruno Olshausen and David Field utilize the above steps to recreate the visual cortex's functionality to improve image recognition. From their perspective, the brain removes redundancy from the information it receives from the photoreceptors and represents the image as a collection of independent events. Previous research in sparse coding focused on 2-dimensional redundancy reduction, which completely omits curves and other higher dimensional collections seen in natural images. To increase the accuracy of existing sparse coding algorithms, Olshausen and Field explore the creation of a linear strategy that can reduce higher order redundancy.

@@

Finding the best set of basis vectors is analogous to creating a model with a probability distribution of each image ($P(I | \phi$)) that matches the probability distribution of images experienced in nature ($P(I^*)$). The Kullback-Leibler divergence is used as their reconstruction error, which is defined as:
\begin{align*}
   KL = \int P^*(I) \log \frac{P^*(I)}{P(I | \phi)} dI
\end{align*}
where it is equal to 0 if and only if the two distributions are equivalent. Since the probability distribution of nature is fixed, Olshausen and Field focus on the log likelihood instead. The optimization function thus becomes:
\begin{align*}
   \phi^* = argmax_\phi [ argmax_a \log P(I | a, \phi) P(a) ]
\end{align*}
and the learning rule for the model is:
\begin{align*}
   \Delta \phi_i (x) = \eta (a_i r(x))
\end{align*}
where $r(x)$ is defined as the residual image, or the difference between the output of the machine and the intended output. While their algorithm is quite accurate compared to other similar models, it is also slow and restricted. It assumes a linear image model, which is not always the case in nature. It also only consists of a single layer, preventing it from being as accurate as possible.

@@

Non-negative Matrix Factorization (NMF) is an algorithm that has been around for several years and was the focus of a paper by Daniel Lee and H. Sebastian Seung. Much like the models previously explored, Lee and Seung use the following equation as the basis for NMF:
\begin{align*}
 V \approx WH
\end{align*}
What makes this particular algorithm standout is its constraint. In fact, the constraint is in its very name - that the matrices in the equation are non-negative. The overall simplicity of this algorithm makes it very simple to implement, despite its increased computation time.

@@

Pascal Vincent, Hugo Larochelle, Isabelle Lajoie, Yoshua Bengio, and Pierre-Antoine Manzagol discuss stacked denoising autoencoders in their 2010 paper, which is a slight modification to the already established autoencoders. Their motivation, much like sparse coding, is to mimic the functions of the visual cortex to enable feature recognition and classification.

The authors describe note one, but two base equations for this model. The first is the encoder, which is defined as:
\begin{align*}
\vy = f_\theta (\vx) = s(\mW \vx + \vb)
\end{align*}
where $\theta = \{ \mW, \vx \}$ are the parameters to be learned. This appears very much like the general equation described at the beginning of this paper as well as to the other models described earlier. The purpose of the encoder is to transform the input into some hidden representation that can later be decoded. Similarly, the decoder is defined as:
\begin{align*}
\vz = g_{\theta^{'}} (\vy) = s(\mW^{'}  \vy + \vb)
\end{align*}
where $\theta^{'} = \{ \mW^{'}, \vb^{'} \}$, $\vy$ is the hidden representation output from the encoder, and $\vz$ is the output of the decoder.

\newpage

\nocite{*}
\bibliographystyle{abbrv}
\bibliography{Paper}
